---
title: "Binning and Adding Color Columns to Ultimate_averages_by_month_longlat"
author: "Zach"
date: "12/2/2024"
output: html_document
---

Making Color Column
```{r}
library(dplyr)

Ultimate_averages_by_month_longlat <- Ultimate_averages_by_month_longlat %>%
  mutate(Color = case_when (
   Average_Min_Price <= 30 ~ "green",
   Average_Min_Price <= 60 ~ "blue",
   Average_Min_Price <= 90 ~ "orange",
   Average_Min_Price <= 120 ~ "red",
   Average_Min_Price > 120 ~ "black"
         )
           )

```


Making New CSV
```{r}
write.csv(Ultimate_averages_by_month_longlat, file = "Ultimate_averages_by_month_longlat.csv")
```


Making Color Column for Other Table
```{r}
Ultimate_with_averages <- Ultimate_with_averages %>%
  mutate(Color = case_when (
   Average_Min_Price <= 30 ~ "green",
   Average_Min_Price <= 60 ~ "blue",
   Average_Min_Price <= 90 ~ "orange",
   Average_Min_Price <= 120 ~ "red",
   Average_Min_Price > 120 ~ "black"
         )
           )
```

Making New CSV
```{r}
write.csv(Ultimate_with_averages, file = "Ultimate_with_averages.csv")
```

Color <- function(Ultimate_with_averages) { 
      sapply(Ultimate_with_averages$Average_Min_Price, 
             function(Average_Min_Price) {
               if (Average_Min_Price <= 30)       {"green"} 
               else if (Average_Min_Price <= 60)  {"blue"}
               else if (Average_Min_Price <= 90)  {"orange"} 
               else if (Average_Min_Price <= 120) {"red"} 
               else {"black"}})}
    
    icons <- awesomeIcons( icon = 'ticket-outline', library = 'ion', markerColor = Color(Ultimate_with_averages))